Hybrid MILP to efficiently and accuratly \\ solve hard DNN verification instances

### 2024-09-24 ICLR25/formula.tex
update formula.tex

Now, consider neurons $a$ two layers before $z$. We use $b$ to denote neurons in the layer between $a$ and $z$. If we open $a$, then the change in the weight of $a$ will still be $\sol(\hat{a})-\ReLU(\sol(a))$ as above. Its impact on $z$ is no more direct with $W_{az}$, but it is through all the $b$ in the intermediate layer. 
Based on Proposition \ref{LP}, we can evaluate how opening $a$ impacts each value of 
$\hat{b}$, through coefficient $k(\hat{b})$, by using the upper and lower bound
$\UB(b),\LB(b)$:
\begin{itemize}
 \item If $W_{bz}\leq0$, then $k(\hat{b})=W_{ab}$ if $\sol(b) > 0$, and $k(\hat{b})=0$ if $\sol(b) < 0$
 \item If $W_{bz}>0$, then $k(\hat{b})=W_{ab} \frac{\UB(b)}{\UB(b)-\LB(b)}$
\end{itemize}
%$\sum_b W_{bz}W_{ab}$ to replace the coefficient $W_{az}$ in last subsection.

%To estimate $\Improve\_\max_a^z$ , 
Indeed, if $W_{bz}\leq0$, then the LP solver sets $\sol(\hat{b})$ to the lowest possible value to maximize $z$, which happens to be $\ReLU(b)$ according to Proposition \ref{LP}.
If $\sol(b) < 0$, then we have a clip at $\sol(\hat{b})=\ReLU(b)=0$ and opening $a$ does not help. If $\sol(b) > 0$, then we have $\sol(\hat{b})=\ReLU(b)=\sol(b)$ and every change from 
$a$ is reflected with a coefficient $W_{ab}$ on $\hat{b}$. 
Last, if $W_{bz}>0$, then according to Proposition \ref{LP}, the LP solver
sets $\sol(\hat{b}) = \sol(b) \frac{\UB(b)}{\UB(b)-\LB(b)}$ to maximize $z$.

@@

We define a difference $\Delta$ to account for the fact that a neuron $b$ 
can not exceed $\LB(b),\UB(b)$:
	\begin{align*}
		&\Delta(\hat{a}) = \sol(\hat{a}) - \ReLU(\sol(a)) \geq 0\\
			&\Delta(\hat{b}) =
		\begin{cases}
			\sol(\hat{b}) - \min(\UB(b), \sol(\hat{b}) - \Delta(\hat{a}) k(\hat{b})), & \text{if }  W_{bz} > 0 \\
			\sol(\hat{b}) - \max(\LB(b), 0, \sol(\hat{b}) -\Delta(\hat{a}) k(\hat{b})), & \text{if }W_{bz} < 0\\
		\end{cases}
		\end{align*}

We can now set

$$ \Utility\_\max\nolimits^z(a) = \sum_b W_{bz} \Delta(\hat{b})$$

>>>>

Now, consider neurons $a$ two layers before $z$. We use $b$ to denote neurons in the layer between $a$ and $z$. If we open $a$, then the change in the weight of $a$ will still be $\sol(\hat{a})-\ReLU(\sol(a))$ as above. Its impact on $z$ is no more direct with $W_{az}$, but it is through all the $b$ in the intermediate layer. 
Based on Proposition \ref{LP}, we can evaluate how opening $a$ impacts each value of 
$\hat{b}$,  by using the upper and lower bound
$\UB(b),\LB(b)$.

Indeed, if $W_{bz}\leq0$, then the LP solver sets $\sol(\hat{b})$ to the lowest possible value to maximize $z$, which happens to be $\ReLU(b)$ according to Proposition \ref{LP}.
If $\sol(b) < 0$, then we have a clip at $\sol(\hat{b})=\ReLU(b)=0$ and opening $a$ does not help. If $\sol(b) > 0$, then we have $\sol(\hat{b})=\ReLU(b)=\sol(b)$ and every change from 
$a$ is reflected with a coefficient $W_{ab}$ on $\hat{b}$. 
Last, if $W_{bz}>0$, then according to Proposition \ref{LP}, the LP solver
sets $\sol(\hat{b}) = \sol(b) \frac{\UB(b)}{\UB(b)-\LB(b)}$ to maximize $z$.

@@

We define a difference $\Delta$ to account for the fact that a neuron $b$ 
can not exceed $\LB(b),\UB(b)$:
	\begin{align*}
		&\Delta(\hat{a}) = \sol(\hat{a}) - \ReLU(\sol(a)) \geq 0\\
		&\Delta(b) = \begin{cases}
			\max(W_{ab}\Delta(\hat{a}),\LB(b)-\sol(b)),  &\text{ if }  W_{ab} < 0 \\
			\min(W_{ab}\Delta(\hat{a}),\UB(b)-\sol(b)),  &\text{ if }  W_{ab} > 0 \\
		\end{cases}\\
			&\Delta(\hat{b}) =
		\begin{cases}
			\max(\Delta(b),-\sol(b)),  &\text{if }  W_{bz} > 0 \text{ and } \sol(b)\geq0\\
				\max(\Delta(b)+\sol(b),0),  &\text{if }  W_{bz} > 0 \text{ and } \sol(b)<0\\
		 \frac{\UB(b)}{\UB(b)-\LB(b)}\Delta(b),  &\text{if }W_{bz} < 0\\
		\end{cases}
		\end{align*}

We can now set 
$$ \Utility\_\max\nolimits^z(a) = \sum_b W_{bz} \Delta(\hat{b}).$$
